### 2015-06-16 writing/S'15 LSTM/discussion.tex
Paper submission candidate.

\begin{figure}[t]
  \centering
      \includegraphics[height=1.1in]{lcc.pdf}
  \caption{Learning curve for the $\le6$ experiment.}
  \label{fig:lc} 
\end{figure}

@@

The results are shown in Figure~\ref{prop-results}. All four models were able to largely memorize the training data (??.?, ??.?, ??.?, and ??.? for $\le$6, pooling across bins). In the $\le$6 setting, the three tree models were able to perform at above ??\% on examples of size $\le$2 with a steady decay in performance continuing through ??.?\% at size 12, and similar, if steeper, decays with smaller training sets. All four robustly beat the simple baselines reported in Bowman et al.: the most frequent class occurs just over 50\% of the time, and a summing model that ignores word order does reasonably on the shortest examples but falls below 60\% by bin 4.

The LSTM performs fairly poorly in the $\le3$ setting, with performance at 3 a mediocre ??.?\%, and an abrupt drop to \% at 4, suggesting that the model did not acquire the needed generalizations. With more ample training data in the $\le6$ condition, though, the LSTM shows fairly good accuracy on short examples, and a smooth decay with no abrupt drop.

@@

We find that all four models can exploit recursive structure to interpret sentences with complex unseen structures, and that tree models' biases allow them to learn to do this more effectively from less data. 
We interpret these results as evidence that the similar performance of tree and sequence models can be attributed to their fundamentally similar representational systems, with both models recognizing compositional structure when it is present, the former doing so more reliably, and the latter benefiting elsewhere---either because of architectural choices that make backpropagation more effective, or because interpreting sentences from left to right allows the model to better simulate other aspects of human language comprehension. We finally suggest that, because of the well supported linguistic claim that the kind of recursive structure that we study here is key to language understanding, there is likely to be value in developing sequence models that can more efficiently exploit this structure without fully sacrificing the flexibility that makes these models succeed.

>>>>

\begin{figure}[t]
  \centering
      \includegraphics[height=1.3in]{lcc.pdf}
  \caption{Learning curve for the $\le$6 experiment.}
  \label{fig:lc} 
\end{figure}

@@

The results are shown in Figure~\ref{prop-results}. 
The tree models fit the training data well, reaching 99.6, 98.5, and 97.7\% overall accuracy respectively in the $\le$6 setting, with the LSTM underfitting slightly at 94.4\%. 
In that setting, all models generalized well to structures of familiar length, with the tree models all surpassing 97\% on examples of size 4, and the LSTM reaching 94.8\%.
On the longer test sentences, the tree models decayed smoothly in performance across the board, while the LSTM decayed more quickly and more abruptly, with a striking difference in the $\le$4 setting, where LSTM performance falls 10\% from 4 to 5, compared to 4.4\% for the next worse model. However, the LSTM improves considerably with more ample training data in the $\le$6 condition, showing only a 3\% drop and generalization results better than the best model's in the $\le$3 setting.  % TODO: These stats?

All four models robustly beat the simple baselines reported in Bowman et al.: the most frequent class occurs just over 50\% of the time and a neural bag of words model does reasonably on the shortest examples but falls below 60\% by bin~4.

@@

We find that all four models can exploit a recursively defined language to interpret sentences with complex unseen structures, and that tree models' biases allow them to learn to do this more effectively from less data.
We interpret these results as evidence that both tree and sequence architectures can play valuable roles in the construction of sentence models over data with recursive syntactic structure: tree architectures provide an explicit bias that makes it possible to learn from relatively small and impoverished data sets, while sequence-based architectures can solve the same problems---given sufficient data---without being constrained by this bias. Finally, we suggest that, because of the well-supported linguistic claim that the kind of recursive structure that we study here is key to the understanding of real natural languages, there is likely to be value in developing sequence models that can more efficiently exploit this structure without fully sacrificing the flexibility that makes them succeed.

### 2015-06-16 writing/S'15 LSTM/methods.tex
Paper submission candidate.

\begin{figure*}[t]
  \centering
  \begin{subfigure}[t]{0.04\textwidth}
      \includegraphics[height=1.45in]{scale.pdf}
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
  \includegraphics[height=1.45in]{fig3c.pdf}
  \caption{Training on sz. $\le$3.}
  \end{subfigure}~~~
\begin{subfigure}[t]{0.24\textwidth}
    \includegraphics[height=1.45in]{fig4c.pdf}
  \caption{Training on sz. $\le$4.}
  \end{subfigure}~~~~
\begin{subfigure}[t]{0.24\textwidth}
      \includegraphics[height=1.45in]{fig6c.pdf}
  \caption{Training on sz. $\le$6.}
\end{subfigure}~~
\begin{subfigure}[t]{0.08\textwidth}
      \includegraphics[height=1.45in]{leg.pdf}
\end{subfigure}
  \caption{Test accuracy on three experiments with increasingly rich training sets. The horizontal axis on each graph divides the test set expression pairs into bins by the number of logical operators in the more complex of the two expressions in the pair. The dotted line shows the size we trained on up to.}
  \label{prop-results} 
\end{figure*}

@@

\paragraph{Training} We randomly initialize all embeddings and layer parameters, and then train all parameters using minibatch stochastic gradient descent with AdaDelta \cite{zeiler2012adadelta} learning rates. Our objective is the standard negative log likelihood classification objective with L2 regularization. All models were stopped after ??? gradient steps, at which point all had largely converged without significantly declining from their peak performances.

>>>>

\begin{figure*}[t]
  \centering
  \begin{subfigure}[t]{0.04\textwidth}
      \includegraphics[height=1.5in]{scale.pdf}
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
  \includegraphics[height=1.5in]{fig3c.pdf}
  \caption{Training on sz. $\le$3.}
  \end{subfigure}~~~~
\begin{subfigure}[t]{0.24\textwidth}
    \includegraphics[height=1.5in]{fig4c.pdf}
  \caption{Training on sz. $\le$4.}
  \end{subfigure}~~~~
\begin{subfigure}[t]{0.24\textwidth}
      \includegraphics[height=1.5in]{fig6c.pdf}
  \caption{Training on sz. $\le$6.}
\end{subfigure}~~
\begin{subfigure}[t]{0.08\textwidth}
      \includegraphics[height=1.5in]{leg.pdf}
\end{subfigure}
  \caption{Test accuracy on three experiments with increasingly rich training sets. The horizontal axis on each graph divides the test set expression pairs into bins by the number of logical operators in the more complex of the two expressions in the pair. The dotted line shows the size we trained on up to.}
  \label{prop-results} 
\end{figure*}

@@

\paragraph{Training} We randomly initialize all embeddings and layer parameters, and train them using minibatch stochastic gradient descent with AdaDelta \cite{zeiler2012adadelta} learning rates. Our objective is the standard negative log likelihood classification objective with L2 regularization (tuned on a separate train/test split). All models were trained for 72 epochs, after which all had largely converged without significantly declining from their peak performances.
